Investigating Fire Incidents Severity Levels in Toronto: Enhancing Resource Allocation for Fire Response

### 2024-12-11 paper/paper.qmd
Edit abtract

We use the statistical programming language R [@citeR]to investigate data about fire incidents[@TFSfireedata], downloaded from the Open Data Toronto Portal: https://open.toronto.ca/dataset/fire-incidents/ . The dataset was last updated on December 31, 2023. It includes fire incidents following the Ontario Fire Marshal's (OFM) definition, with descriptions according to OFM standards. The dataset also provides detailed information on Toronto Fire Services' (TFS) responses to each fire incident. The data is mostly complete, though some incidents are still under investigation and categorized as "no loss outdoor fire." The dataset includes information on the origin of fires, impacts on civilians and buildings, as well as geographical data (see @tbl-preview-data). Additionally, it contains details on TFS response times and actions taken. Overall, the dataset is comprehensive, informative, and provides valuable insights for my later study.

>>>>

We use the statistical programming language R [@citeR]to investigate data about fire incidents, downloaded from the Open Data Toronto Portal [@OpenDataToronto], named [Fire Incidents](https://open.toronto.ca/dataset/fire-incidents/) [@TFSfireedata]. The dataset was last updated on December 31, 2023. It includes fire incidents following the Ontario Fire Marshal's (OFM) definition, with descriptions according to OFM standards. The dataset also provides detailed information on Toronto Fire Services' (TFS) responses to each fire incident. The data is mostly complete, though some incidents are still under investigation and categorized as "no loss outdoor fire." The dataset includes information on the origin of fires, impacts on civilians and buildings, as well as geographical data (see @tbl-preview-data). Additionally, it contains details on TFS response times and actions taken. Overall, the dataset is comprehensive, informative, and provides valuable insights for my later study.
